Prehensile Manipulation Planning: Modelling, Algorithms and Implementation

### 2021-05-21 hpp.tex
Fix equations of ConvexShapeContact.

We denote by $o_i(\conf)$ and $f_j(\conf)$ the poses in configuration $\conf$ of frames with respective centers $C_{o_i}$ and $C_{f_j}$ and with $x$-axis normal to each polygon. In an analogous way as in Definition~\ref{def:grasp}, we define
\begin{equation}\label{eq:convex-shape-contact-hbar}
\bar{h}(\conf) = \log_{\reals^3\times SO(3)} \left(f_{j}(\conf)^{-1}o_i(\conf)\right)
\end{equation}
The contact constraint is defined by the following piece-wise differentiable function:
\begin{equation}\label{eq:convex-shape-contact}
h(\conf) = \left\{\begin{array}{lll}(\bar{h}_1,0,0,\bar{h}_4,\bar{h}_5)&
\mbox{if} & P(C_{o_i},f_j)\mbox{ inside } f_j\\
(\bar{h}_1,\bar{h}_2,\bar{h}_3,\bar{h}_4,\bar{h}_5)&
\mbox{if} & P(C_{o_i},f_j)\mbox{ outside } f_j\end{array}\right.
\end{equation}
It is straightforward that the above function vanishes if and only if two convex polygons $o_i$ and $f_j$ are in contact and $C_{o_i}$ is inside $f_j$.

As for grasps, we need to define a parameterized complement constraint for the contact constraint in order to specify the sub-manifold of configurations that are reachable from one configuration while keeping the object in a constant stable pose. The naive way consists in defining
$$
h_{comp}(\conf) = \left\{\begin{array}{lll}(\bar{h}_2,\bar{h}_3,\bar{h}_6)&
\mbox{if} & P(C_{o_i},f_j)\mbox{ inside } f_j\\
(0,0,\bar{h}_6)&
\mbox{if} & P(C_{o_i},f_j)\mbox{ outside } f_j\end{array}\right.
$$
$\bar{h}_2$, $\bar{h}_3$, $\bar{h}_6$ respectively represent the translation in $x-y$ plane and the rotation around $z$-axis of frame $o_i$ with respect to frame $f_j$. Let $\conf_0$ be a configuration such that $h(\conf_0)=0$. The sub-manifold defined by
\begin{equation}\label{eq:stable-pose}
\left\{\conf\in\CS,\ \ h(\conf)=0\ \ h_{comp}(\conf) = h_{comp}(\conf_0) \right\}
\end{equation}
contains one object pose for each pair of polygons $(o_i,f_j)$, and there are
$|I| . |J|$ possible combinations. This constraint is therefore not suitable to
enforce object immobility along a path since the object may jump from one pose to another one.

To disambiguate the various combination of convex polygons that can be in contact, we define
\begin{equation}\label{eq:convex-shape-contact-complement}
h_{comp}(\conf) = \left\{\begin{array}{l}(\bar{h}_2 + 2jM,\bar{h}_3 + 2iM,\bar{h}_6)\\
\mbox{if } P(C_{o_i},f_j)\mbox{ inside } f_j\\
(2jM,2iM,\bar{h}_6)\\
\mbox{if } P(C_{o_i},f_j)\mbox{ outside } f_j\end{array}\right.
\end{equation}
where
\begin{itemize}
\item $i$ and $j$ are the indices that minimize distance~(\ref{eq:contact-distance}),
\item $M$ is a positive real number such that for any $\kappa\in J$, all vertices of $f_\kappa$ are included in the disk of center $C_{f_\kappa}$ and of radius $M$.
\end{itemize}
With this definition, the sub-manifold defined by~(\ref{eq:stable-pose}), (\ref{eq:convex-shape-contact}), (\ref{eq:convex-shape-contact-complement}) contains configurations where the object is in a unique stable pose. The polygon indices $i$ and $j$, as well as their relative position can indeed be recovered from~(\ref{eq:convex-shape-contact-complement}):
\begin{align*}
  i &= \left\lfloor\frac{\bar{h}_3}{2M} + \frac{1}{2}\right\rfloor\\
  j &= \left\lfloor\frac{\bar{h}_2}{2M} + \frac{1}{2}\right\rfloor\\
  \bar{h}_1 &= \bar{h}_4 = \bar{h}_5 = 0\\
  \bar{h}_2 &= h_{comp\ 1} - 2jM\\
  \bar{h}_3 &= h_{comp\ 2} - 2iM\\
  \bar{h}_6 &= h_{comp\ 3}
\end{align*}
and from (\ref{eq:convex-shape-contact-hbar}),
$$
f_{j}(\conf)^{-1}o_i(\conf) = \exp_{\reals^3\times SO(3)}\left(\bar{h}\right).
$$
Uniqueness comes from the fact that when two convex polygons are in contact,
necessarily, $|\bar{h}_2| \leq M$,$|\bar{h}_3| \leq M$.
% Remark about convergence of the solver and about explicit constraint.

>>>>

We denote by $o_i(\conf)$ and $f_j(\conf)$ the poses in configuration $\conf$ of frames with respective centers $C_{o_i}$ and $C_{f_j}$ and with $x$-axis normal to each polygon. In an analogous way as in Definition~\ref{def:grasp}, we define
\begin{equation}\label{eq:convex-shape-contact-hbar}
\bar{h}(\conf) = \log_{\reals^3\times SO(3)} \left(f_{j}(\conf)^{-1}o_i(\conf)\right)
\end{equation}
The contact constraint is defined by the following piece-wise differentiable function:
\begin{equation}\label{eq:convex-shape-contact}
h(\conf) = \left\{\begin{array}{lll}(\bar{h}_1,0,0,\bar{h}_5,\bar{h}_6)&
\mbox{if} & P(C_{o_i},f_j)\mbox{ inside } f_j\\
(\bar{h}_1,\bar{h}_2,\bar{h}_3,\bar{h}_5,\bar{h}_6)&
\mbox{if} & P(C_{o_i},f_j)\mbox{ outside } f_j\end{array}\right.
\end{equation}
It is straightforward that the above function vanishes if and only if two convex polygons $o_i$ and $f_j$ are in contact and $C_{o_i}$ is inside $f_j$.

As for grasps, we need to define a parameterized complement constraint for the contact constraint in order to specify the sub-manifold of configurations that are reachable from one configuration while keeping the object in a constant stable pose. The naive way consists in defining
$$
h_{comp}(\conf) = \left\{\begin{array}{lll}(\bar{h}_2,\bar{h}_3,\bar{h}_4)&
\mbox{if} & P(C_{o_i},f_j)\mbox{ inside } f_j\\
(0,0,\bar{h}_4)&
\mbox{if} & P(C_{o_i},f_j)\mbox{ outside } f_j\end{array}\right.
$$
$\bar{h}_2$, $\bar{h}_3$, $\bar{h}_4$ respectively represent the translation in $y-z$ plane and the rotation around $x$-axis of frame $o_i$ with respect to frame $f_j$. Let $\conf_0$ be a configuration such that $h(\conf_0)=0$. The sub-manifold defined by
\begin{equation}\label{eq:stable-pose}
\left\{\conf\in\CS,\ \ h(\conf)=0\ \ h_{comp}(\conf) = h_{comp}(\conf_0) \right\}
\end{equation}
contains one object pose for each pair of polygons $(o_i,f_j)$, and there are
$|I| . |J|$ possible combinations. This constraint is therefore not suitable to
enforce object immobility along a path since the object may jump from one pose to another one.

To disambiguate the various combinations of convex polygons that can be in contact, we define
\begin{equation}\label{eq:convex-shape-contact-complement}
h_{comp}(\conf) = \left\{\begin{array}{l}(\bar{h}_2 + 2jM,\bar{h}_3 + 2iM,\bar{h}_4)\\
\mbox{if } P(C_{o_i},f_j)\mbox{ inside } f_j\\
(2jM,2iM,\bar{h}_4)\\
\mbox{if } P(C_{o_i},f_j)\mbox{ outside } f_j\end{array}\right.
\end{equation}
where
\begin{itemize}
\item $i$ and $j$ are the indices that minimize distance~(\ref{eq:contact-distance}),
\item $M$ is a positive real number such that for any $\kappa\in J$, all vertices of $f_\kappa$ are included in the disk of center $C_{f_\kappa}$ and of radius $M$.
\end{itemize}
With this definition, the sub-manifold defined by~(\ref{eq:stable-pose}), (\ref{eq:convex-shape-contact}), (\ref{eq:convex-shape-contact-complement}) contains configurations where the object is in a unique stable pose. The polygon indices $i$ and $j$, as well as their relative position can indeed be recovered from~(\ref{eq:convex-shape-contact-complement}):
\begin{align*}
  i &= \left\lfloor\frac{\bar{h}_3}{2M} + \frac{1}{2}\right\rfloor\\
  j &= \left\lfloor\frac{\bar{h}_2}{2M} + \frac{1}{2}\right\rfloor\\
  \bar{h}_1 &= \bar{h}_5 = \bar{h}_6 = 0\\
  \bar{h}_2 &= h_{comp\ 1} - 2jM\\
  \bar{h}_3 &= h_{comp\ 2} - 2iM\\
  \bar{h}_4 &= h_{comp\ 3}
\end{align*}
and from (\ref{eq:convex-shape-contact-hbar}),
$$
f_{j}(\conf)^{-1}o_i(\conf) = \exp_{\reals^3\times SO(3)}\left(\bar{h}\right).
$$
Uniqueness comes from the fact that when two convex polygons are in contact,
necessarily, $|\bar{h}_2| \leq M$,$|\bar{h}_3| \leq M$.
% Remark about convergence of the solver and about explicit constraint.
